The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-12-09 reviews/initial-response.tex
Adress editor comment on geothermal heat flux

>>>>

Thank you for raising this point. A justification was added in the manuscript. In this study, we focus mainly on glacier extent, on which geothermal heat flux is not the major control. However we will be happy to add a sensitivity experiment to the paper if this point is risen again at the discussion stage.

### 2013-12-09 sections/model.tex
Adress editor comment on geothermal heat flux

The Shallow Shelf Approximation (SSA) is used as a ``sliding law'' for the Shallow Ice Approximation (SIA) \citep{bueler-brown-2009,winkelmann-etal-2011}. SIA and SSA velocities are computed by finite difference methods on a 10\,km-resolution horizontal grid of 300 by 150 points (the modelling domain). Ice softness depends on temperature and water content through an enthalpy formulation \citep{aschwanden-blatter-2009,aschwanden-etal-2012}. Enthalpy is computed in three dimensions in up to 51 irregularly spaced layers within the ice, and temperature is additionally computed in 11 regularly spaced layers in bedrock to a depth of 1\,km. A uniform geothermal heat flux of 70\,\unit{W\,m^{-2}} provides the lower boundary condition to the bedrock thermal model, and surface air temperature from the climate forcing provides the upper boundary condition to the ice enthalpy model.

>>>>

The Shallow Shelf Approximation (SSA) is used as a ``sliding law'' for the Shallow Ice Approximation (SIA) \citep{bueler-brown-2009,winkelmann-etal-2011}. SIA and SSA velocities are computed by finite difference methods on a 10\,km-resolution horizontal grid of 300 by 150 points (the modelling domain). Ice softness depends on temperature and water content through an enthalpy formulation \citep{aschwanden-blatter-2009,aschwanden-etal-2012}. Enthalpy is computed in three dimensions in up to 51 irregularly spaced layers within the ice, and temperature is additionally computed in 11 regularly spaced layers in bedrock to a depth of 1\,km. Surface air temperature from the climate forcing provides the upper boundary condition to the ice enthalpy model, and a geothermal heat flux of 70\,\unit{mW\,m^{-2}} provides the lower boundary condition to the bedrock thermal model. Although this uniform value does not account for the high spatial geothermal variability of the region \citep{blackwell-richards-2004}, it is on average representative of available heat flow measurements \citep{artemieva-mooney-2001,blackwell-richards-2004}. In addition, whereas spatial variations of geothermal heat flux may significantly affect basal conditions of ice sheets \citep{pattyn-2010}, this study focuses on reconstructing the former extent of ice cover, on which it has relatively little effect \citep{rogozhina-etal-2012}.
